---
title: "Getting Started With BioCroValidation"
output:
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{Getting Started With BioCroValidation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 5,
  fig.align = "center"
)
```

# Overview

**BioCroValidation** is an R package that provides a suite of tools for
validating BioCro crop growth models.

Validation is a key part of using and developing BioCro models. The goal of this
package is to provide some convenient "helping" functions to aid with various
aspects of model validation, especially parameterization.

The central tool in the package is the `objective_function` function. As its
name implies, it can be used to create an objective function that calculates the
value of an error metric value given a set of model parameter values. In turn,
the objective function itself can be passed to an optimizer.

While it is possible for each BioCro user to write their own customized
objective function, creating one can be a very complex process because there are
many potential aspects to consider:

- **Mathematical / Statistical Approach:** This refers to choices like "Do I
  want to normalize the error terms by each observed value, or by the largest
  observed value for each measured quantity?" or "Do I want to use L1 or L2
  regularization?"

- **Implementation of Mathematical / Statistical Approach:** Once an approach
  has been identified, code must be written to properly implement it.

- **Error Checks:** A wide variety of strange conditions can occur during
  parameterization, and the objective function must be ready to handle them. For
  example, how should the objective function respond when a simulation does not
  run to completion, or when an optimizer passes `NA` as a parameter value?

- **Technical Details:** Parameterization can take a long time to perform, so it
  is important for the objective function code to be as efficient and fast as
  possible.

The goal of `objective_function` is to allow users to make the key choices about
their mathematical approach using clear code statements like
`regularization_method = 'L2'`, while the implementation details, error checks,
and other technical details are handled internally. This will result in clear
scripts that are also more reliable.

Besides `objective_function`, the package also includes a few other functions
with a similar goal of clarifying code and hiding implementation details, such
as `bounds_table` and `update_model`.

# Installing BioCroValidation

The easiest way to install `BioCroValidation` is to type the following from
within an R terminal:

```{r, eval = FALSE}
remotes::install_github('biocro/BioCroValidation')
```

Note that this method requires the `remotes` package, which can be installed
from within R by typing `install.packages('remotes')`.

# Learning More

The `BioCroValidation` package includes extensive documentation. The best place
to start is the
[Parameterizing Soybean-BioCro](parameterizing_soybean_biocro.html)
article, which illustrates the full process of defining an objective function,
running an optimization, examining the results, and saving the new model
definition.

Another key resource is the help page for `objective_function`, which can be
accessed online or by typing `?objective_function` in an R terminal. This
document explains all the available options for normalization approaches,
regularization approaches, and other aspects of defining an objective function.
