---
title: "Parameterizing Soybean-BioCro"
output:
  rmarkdown::html_vignette:
    toc: true
    number_sections: true
vignette: >
  %\VignetteIndexEntry{Parameterizing Soybean-BioCro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib
link-citations: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7.5,
  fig.height = 5,
  fig.align = "center"
)
```

# Overview

This article shows how to create an objective function that can be used to
parameterize BioCro's soybean model
[@matthews_soybean_biocro_2021; @lochocki_biocro_2022].

Since the original publication of Soybean-BioCro, the BioCro module library has
undergone several changes, and the model has been re-parameterized several
times. These parameterizations did not use `BioCroValidation`, since they were
performed before `BioCroValidation` was created.

However, `BioCroValidation` is able to re-create the objective functions that
were used for these parameterizations. Here, we re-create the objective function
that was used for the parameterization included in version `3.2.0` of the BioCro
R package.

In the commands below, we will use functions from several libraries, so we will
load them now:

```{r libraries}
# Load required libraries
library(BioCroValidation)
library(BioCro)
library(dfoptim)
library(lattice)
```

# Building the Objective Function

In this section, we will use the `objective_function` function from
`BioCroValidation` package to create an objective function that can be used to
parameterize Soybean-BioCro. For more details about this, please see the help
page for `objective_function` by typing `?objective_function` from an R
terminal.

## The Base Model Definition

We first need a base model definition that includes the necessary modules,
initial values, parameters, and differential equation solver specifications. For
this example, we will simply use Soybean-BioCro as the base model, with just one
small change: we will use an Euler solver rather than the default solver, which
will help make the optimization run faster. For reasonable sets of parameter
values, the Euler solver does not seem to cause any substantial errors when
running Soybean-BioCro.

```{r base_model_definition}
# Specify the base model definition
base_model_definition            <- soybean
base_model_definition$ode_solver <- default_ode_solvers[['homemade_euler']]
```

## The Observed Data

The observed data needed to parameterize Soybean-BioCro is included in the
`BioCroValidation` package as the `soyface_biomass` data set, which consists of
two years (2002 and 2005) of biomass data and associated standard deviations,
included in four separate tables. However, each table requires some
pre-processing to get it ready.

One issue is that the data set specifies the doy of year (DOY) for each harvest,
but we need to specify the time using BioCro's convention (the number of hours
since the start of the year).

Another issue is that the data set includes pod and seed values, but
Soybean-BioCro calculates shell and seed masses, where the shell and seed
together comprise the pod.

Although the observations do not include root biomass, it is nevertheless
important to constrain the predicted root mass to reasonable values. To do this,
it is assumed that the maximum root mass is seventeen percent of the maximum
aboveground biomass, and that it is achieved at the same time as maximum
above-ground biomass, based on observations reported in @ordonez_root_2020. In
the observed data, the sum of stem and leaf mass is largest at the fifth time
point in both years. So, root mass is estimated at this single time point and
added to the observed values.

In previous parameterizations, a standard deviation for the root mass was not
explicitly estimated; instead, the standard-deviation-based weight factor was
implicitly set to 1. Because the `'logarithm'` method with
\(\epsilon = 10^{-5}\) was used, a weight factor of 1 implies a standard
deviation of \(1 / e - 10^{-5} \approx 0.3678694\). See the documentation page
(`?objective_function`) for more information about this weighting method.

Finally, the data set includes some values that are not needed for the
parameterization. This includes the leaf litter accumulated between each
harvest, as well as the `DOY` and `Rep_Mg_per_ha` columns that have been
superseded by other columns defined above.

Here we will define a helping function that can accomplish the required
modifications described above; note that some operations are different depending
on whether the table represents biomass values or standard deviations:

```{r process_tables}
# Define a helping function for processing data tables
process_table <- function(data_table, type) {
  # Define new `time` column
  data_table$time <- (data_table$DOY - 1) * 24.0

  # Define new `Shell_Mg_per_ha` column
  data_table$Shell_Mg_per_ha <- if (type == 'biomass') {
    # The shell is all parts of the pod other than the seed
    data_table$Rep_Mg_per_ha - data_table$Seed_Mg_per_ha
  } else {
    # Add uncertainties in quadrature, a simple approach to error propagation
    sqrt(data_table$Rep_Mg_per_ha^2 + data_table$Seed_Mg_per_ha^2)
  }

  # Define new `Root_Mg_per_ha` column, which has just one non-NA value
  row_to_use <- 5                 # Choose row to use
  data_table$Root_Mg_per_ha <- NA # Initialize all values to NA

  if (type == 'biomass') {
    # Estimate a mass at one time point
    col_to_add <- c(
      'Leaf_Mg_per_ha',
      'Stem_Mg_per_ha',
      'Rep_Mg_per_ha'
    )

    data_table[row_to_use, 'Root_Mg_per_ha'] <-
      0.17 * sum(data_table[row_to_use, col_to_add])
  } else {
    # Estimate standard deviation at one time point
    data_table[row_to_use, 'Root_Mg_per_ha'] <- 1 / exp(1) - 1e-5
  }

  # Remove columns by setting them to NULL
  data_table$DOY              = NULL
  data_table$Rep_Mg_per_ha    = NULL
  data_table$Litter_Mg_per_ha = NULL

  # Return the processed table
  data_table
}
```

## The Data-Driver Pairs

The `BioCro` R package includes weather data for the years in the
`soyface_biomass` data set. So now we are ready to define the data-driver pairs,
which includes the weather, the observed biomass, the standard deviation of the
observed biomass, and the weight to assign to each year:

```{r data_driver_pairs}
# Define the data-driver pairs
data_driver_pairs <- list(
  ambient_2002 = list(
    data       = process_table(soyface_biomass[['ambient_2002']],     'biomass'),
    data_stdev = process_table(soyface_biomass[['ambient_2002_std']], 'stdev'),
    drivers    = BioCro::soybean_weather[['2002']],
    weight     = 1
  ),
  ambient_2005 = list(
    data       = process_table(soyface_biomass[['ambient_2005']],     'biomass'),
    data_stdev = process_table(soyface_biomass[['ambient_2005_std']], 'stdev'),
    drivers    = BioCro::soybean_weather[['2005']],
    weight     = 1
  )
)
```

Here we have chosen equal weights for the two years.

## The Post-Processing Function

The observed data includes values of the total litter, which is comprised of
both leaf and stem litter. However, the model does not calculate this quntity;
instead, it returns separate values of leaf and stem litter. To address this
issue, we can provide a "post-processing function." This is an (optional)
function that is applied to each simulation result and can be used to add new
columns. Here we define such a function, which adds a new column for the total
litter:

```{r post_process_function}
# Define the post-processing function
post_process_function <- function(sim_res) {
  # Calculate the total litter as the sum of leaf and stem litter
  within(sim_res, {TotalLitter = LeafLitter + StemLitter})
}
```

## The Data Definitions

The data sets above have columns whose names do not match the corresponding
model outputs. For example, the `Leaf_Mg_per_ha` column of the observed data
must be compared to the `Leaf` column of the model output, since both represent
the leaf mass per unit ground area. To handle this mismatch, we can provide a
set of "data definitions" that specify which columns should be compared:

```{r data_definitions}
# Define the data definition list, where the element names are columns in the
# observed data tables, and the element values are the corresponding column
# names in the model outputs
data_definitions <- list(
# Observed               Simulated
  CumLitter_Mg_per_ha = 'TotalLitter',
  Leaf_Mg_per_ha      = 'Leaf',
  Root_Mg_per_ha      = 'Root',
  Seed_Mg_per_ha      = 'Grain',
  Shell_Mg_per_ha     = 'Shell',
  Stem_Mg_per_ha      = 'Stem'
)
```

## The Arguments to Vary

Here we wish to vary several parameters related to carbon partitioning for
growth, senescence, maintenance respiration, and growth respiration:

- For each growing tissue, there are two parameters (\(\alpha\) and \(\beta\))
  that influence the parbon partitioning coefficients. Here we will vary these
  for the leaf, stem, and shell (6 parameters in total).

- For each senescing tissue, there are three parameters (\(\alpha_{sen}\),
  \(\beta_{sen}\), and `rate`) that influence when senescence begins and
  the overall rate of scenescence. Here we will vary these for the leaf and stem
  (6 parameters in total).

- For each growing tissue, there is one parameter (`grc`) that influences the
  rate of carbon use for growth respiration. Here we will vary these for the
  stem and root (2 parameters in total).

- For each tissue, there is one parameter (`mrc`) that influences the rate of
  carbon use for maintenance respiration. Here we will vary these for the leaf,
  stem, and root (3 parameters in total).

Together, this is 17 arguments to vary. Typically, an optimization problem
requires more time for each free parameter involved, so it is helpful to vary
the smallest possible set. One way to reduce the number of free parameters is to
treat some as being "dependent." In other words, to calculate the values of some
parameters from the values of others, so that only some of them are truly free
or "independent." Here we will do this by fixing the value of `mrc_stem` to the
value of `mrc_leaf`. Thus, we can think of this is a single maintenance
respiration coefficient for the entire shoot; this reduces the number of
independent parameters by one (to 16).

The independent arguments must be specified as a list of named numeric elements,
where the name is the argument name and the value is an initial guess for that
argument. Here we will use the default Soybean-BioCro values as our initial
guesses:

```{r independent_args}
# Define a list of independent arguments and their initial values
independent_arg_names <- c(
  # Partitioning for leaf, stem, and shell
  'alphaLeaf',
  'betaLeaf',
  'alphaStem',
  'betaStem',
  'alphaShell',
  'betaShell',

  # Senescence for leaf and stem
  'alphaSeneLeaf',
  'betaSeneLeaf',
  'rateSeneLeaf',
  'alphaSeneStem',
  'betaSeneStem',
  'rateSeneStem',

  # Growth respiration for stem and root
  'grc_stem',
  'grc_root',

  # Maintenance respiration for leaf and root
  'mrc_leaf',
  'mrc_root'
)

independent_args <- soybean$parameters[independent_arg_names]
```

The dependent arguments must be specified as a function that takes a list of
independent arguments as its input, and returns a list of dependent arguments as
its output:

```{r dependent_arg_function}
# Define a function that sets `mrc_stem` to the value of `mrc_leaf`
dependent_arg_function <- function(ind_args) {
  list(mrc_stem = ind_args[['mrc_leaf']])
}
```

## The Quantity Weights

When determining the error metric value, we wish to assign different weights to
each type of observed value. This can be handled via the `quantity_weights`,
which must be a list of named numeric elements, where the name of each element
is an output from the simulation, and its value is the weight.

```{r quantity_weights}
# Specify the quantity weights; there is no systematic way to determine these,
# but the following weights have worked well in the past for Soybean-BioCro
quantity_weights <- list(
  Grain       = 1.0,
  Leaf        = 1.0,
  Root        = 0.1,
  Shell       = 0.5,
  Stem        = 1.0,
  TotalLitter = 0.1
)
```

## The Extra Penalty Function

Sometimes an optimizer may choose parameter values that produce close agreement
with the observed data but are nevertheless unreasonable from a biological
perspective.

To prevent these unreasonable parameters from being chosen, "extra penalties"
can be added to the error metric. These penalties can be specified using an
`extra_penalty_function`, which must take the result from a BioCro simulation
as its input and return a numeric error penalty value, which generally should be
zero (when no issues are found) or a large positive number (if an issue has been
found).

For Soybean-BioCro parameterization, three common issues are that:

1. Carbon is never partitioned to one or more key tissues.

2. Carbon partitioning to the stem and leaf starts at different times.

3. Carbon partitioning to the leaves begins too early or too late.

The function below will return a large value when any of these situations
occurs, and will otherwise return a value of zero.

```{r extra_penalty_function}
# Define an extra penalty function
extra_penalty_function <- function(sim_res) {
  # Set the penalty value
  PENALTY <- 9999

  # Get the first times when each partitioning coefficient becomes non-zero
  k_thresh <- 0.01 # Threshold k value to decide when growth has started
  hpd      <- 24.0 # Hours per day

  time <- sim_res[['time']]

  time_grain <- time[sim_res[['kGrain']] > k_thresh][1]
  time_leaf  <- time[sim_res[['kLeaf']]  > k_thresh][1]
  time_shell <- time[sim_res[['kShell']] > k_thresh][1]
  time_stem  <- time[sim_res[['kStem']]  > k_thresh][1]

  # Return a penalty if necessary
  if (is.na(time_grain) | is.na(time_leaf) | is.na(time_shell) | is.na(time_stem)) {
    # One or more tissues is not growing
    return(PENALTY)
  } else if (abs(time_leaf - time_stem) > 5 * hpd) {
    # The starts of leaf and stem growth are more than 5 days apart
    return(PENALTY)
  } else if (time_leaf - time[1] > 20 * hpd | time_leaf - time[1] < 10 * hpd) {
    # The start of leaf growth is too late (more than 20 days after sowing) or
    # too early (fewer than 10 days after sowing)
    return(PENALTY)
  } else {
    # No problems were detected
    return(0.0)
  }
}
```

## The Objective Function

Now we are just about ready to build the objective function. There are a few
more details to discuss:

- Soybean-BioCro has always used the `'mean_max'` method for determining
  normalization factors; see Equations 14-16 of @matthews_soybean_biocro_2021
  for more details.

- Soybean-BioCro has always used the `'logarithm'` method for determining
  weights from standard deviations with \(\epsilon = 10^{-5}\); see Equation 17
  of @matthews_soybean_biocro_2021 for more details.

- Soybean-BioCro has not used any regularization.

With this, it is possible to build the function. Note that some useful
information is printed out when the function is created, such as the full list
of observed values and their corresponding weights.

```{r objective_function}
# Create the objective function
obj_fun <- objective_function(
  base_model_definition,
  data_driver_pairs,
  independent_args,
  quantity_weights,
  data_definitions       = data_definitions,
  normalization_method   = 'mean_max',
  stdev_weight_method    = 'logarithm',
  stdev_weight_param     = 1e-5,
  regularization_method  = 'none',
  dependent_arg_function = dependent_arg_function,
  post_process_function  = post_process_function,
  extra_penalty_function = extra_penalty_function
)
```

# Optimizing the Parameter Values

The objective function is designed to be passed to a minimization algorithm,
which will determine the argument values that produce the best agreement between
the model predictions and the observations.

Soybean-BioCro has already been parameterized, so there is already good
agreement between the model and the data. This can be seen by examining the
value of the error metric when using the default Soybean-BioCro values:

```{r}
# Evaluate the error function with default Soybean-BioCro parameters
default_error <- obj_fun(as.numeric(independent_args))
```

This evaluates to `r default_error`. This is a low value for a Soybean-BioCro
parameterization, indicating that good agreement has already been found.

Here, as an example, we will intentionally change each parameter value by a
small random amount, and then use an optimizer to improve the parameter values;
in an ideal world, the optimizer will eventually pick parameter values close to
the original Soybean-BioCro values.

There are many optimizers available in R. Base R includes the `optim` function,
and others are available from the `dfoptim` and `DEoptim` packages. Here we will
use the `nmkb` optimizer from the `dfoptim` library, which requires upper and
lower bounds for each parameter and an initial guess.

## Choosing an Initial Guess

As mentioned above, we will intentionally choose a "bad" initial guess by
tweaking each parameter value by a small random amount. Note that we set a seed
to ensure the same result is obtained every time this is performed. Also note
that the initial guess must be a numeric vector, where the elements are ordered
as they are in `independent_args`.

```{r initial_guess}
# Set a seed
set.seed(1234)

# Make an initial guess by perturbing the default values by a small amount
rel_size <- 0.02

initial_guess <- as.numeric(independent_args) *
  (1.0 + runif(length(independent_args), -rel_size, rel_size))
```

Even though the changes to parameter values are small, there is still a
substantial change in the value of the error metric:

```{r}
# Evaluate the error function with default Soybean-BioCro parameters
initial_error <- obj_fun(initial_guess)
```

This evaluates to `r initial_error`, which is about
`r round(100 * (initial_error - default_error) / initial_error)` percent larger
than with the default parameter values.

## Choosing Lower and Upper Bounds

There is not always a systematic approach to choosing lower and upper bounds for
parameter values, but the following bounds have worked well for Soybean-BioCro
in the past:

- The \(\alpha\) parameters used in partitioning and senescence calculations are
  confined to the interval [0, 50].

- The \(\beta\) parameters used in partitioning and senescence calculations are
  confined to the interval [-50, 0].

- The senescence rates have a lower bound of zero, but have different upper
  bounds for each tissue.

- The maintenance respiration coefficients are confined to the interval
  [1e-6, 1e-2].

- The growth respiration coefficients must be positive and non-zero, but have
  different bounds for each tissue.

There are many possible ways to specify the bounds in R, but ultimately they
must be expressed as numeric vectors, where the elements are ordered as they are
in `independent_args`. Here we use the `bounds_table` function from
`BioCroValidation` to create a data frame where the lower and upper bounds are
stored as columns. Later, the columns can be passed to the optimizer. The
`bounds_table` function will also check the initial guess to ensure it lies
within the bounds; for more information about this function, see its help page
by typing `?bounds_table` from an R terminal.

```{r setting_bounds}
# Specify some bounds
aul <- 50   # Upper limit for alpha parameters
bll <- -50  # Lower limit for beta parameters
mll <- 1e-6 # Lower limit for mrc parameters
mul <- 1e-2 # Upper limit for mrc parameters

# Define a table with the bounds in the same order as `independent_args`
bounds <- bounds_table(
  independent_args,
  list(
    alphaLeaf     = c(0,      aul),
    alphaStem     = c(0,      aul),
    alphaShell    = c(0,      aul),
    alphaSeneLeaf = c(0,      aul),
    alphaSeneStem = c(0,      aul),
    betaLeaf      = c(bll,    0),
    betaStem      = c(bll,    0),
    betaShell     = c(bll,    0),
    betaSeneLeaf  = c(bll,    0),
    betaSeneStem  = c(bll,    0),
    rateSeneLeaf  = c(0,      0.0125),
    rateSeneStem  = c(0,      0.005),
    mrc_leaf      = c(mll,    mul),
    mrc_root      = c(mll,    mul),
    grc_stem      = c(8e-4,   0.08),
    grc_root      = c(0.0025, 0.075)
  ),
  initial_guess
)
```

## Running the Optimizer

Now we will use an optimizer to improve on the initial guess. As mentioned
above, we will use the `nmkb` optimizer from the `dfoptim` package. This is a
good choice when a decent starting guess is known. If a broader search is
necessary, `DEoptim` from the `DEoptim` package may be more appropriate,
although it generally needs more time to run.

To make sure this example does not take too much time, we will use a loose
tolerance; a more realistic example would probably use `1e-4` or `1e-5`.

```{r run_optimizer, eval = FALSE}
# Run the optimizer
optim_res <- nmkb(
  initial_guess,
  obj_fun,
  bounds[['lower']],
  bounds[['upper']],
  control = list(
    tol = 1e-2,
    restarts.max = 10
  ),
  debug_mode = FALSE # Passed to obj_fun; set to TRUE to enable debug mode
)
```

```{r, echo = FALSE}
timing <- system.time({
<<run_optimizer>>
})
```

When this document was generated, running the optimizer required the following
amount of time:

```{r, echo = FALSE}
print(timing)
```

The total time was about `r round(timing[3] / 60, 2)` minutes. For a real
parameterization problem, it can be many times longer, and may even need days to
run on a personal laptop computer.

The optimizer also reports how many times the objective function was called,
among other details:

```{r}
str(optim_res)
```

The value of `feval` is `r optim_res[['feval']]`, so on average, each call of
the objective function required approximately
`r round(timing[3] / optim_res[['feval']], 3)` seconds.

## Comparing Parameter Values

Let's see whether the optimized parameters are closer to the default parameters
than the initial guess was.

```{r compare_param}
# Create a table of the various independent argument values
ind_arg_table <- data.frame(
  arg_name      = independent_arg_names,
  defaults      = as.numeric(independent_args),
  initial_guess = initial_guess,
  optimized     = optim_res[['par']],
  stringsAsFactors = FALSE
)

# Add differences
ind_arg_table <- within(ind_arg_table, {
  initial_diff   = abs(initial_guess - defaults)
  optimized_diff = abs(optimized - defaults)
  improved       = optimized_diff < initial_diff
})

# View results
print(ind_arg_table)
```

In this table, when the `improved` column is `TRUE`, this means that the
optimized parameter value is closer to the default value than the initial guess
was; in other words, it means that the optimizer truly improved on the initial
guess. In this example, `r sum(ind_arg_table[['improved']])` out of
`r nrow(ind_arg_table)` parameter estimates were improved
(`r round(100 * sum(ind_arg_table[['improved']]) / nrow(ind_arg_table))` percent).

We can also compare the error metric to its original value. As shown above, it
is now `r optim_res[['value']]`, which is only
`r round(100 * (optim_res[['value']] - default_error) / optim_res[['value']], 1)`
percent larger than with the default parameter values.

The optimized parameter values could likely be improved by using a more
stringent tolerance for the optimizer, but this would require more time to run.

## Comparing Model Outputs

Another way to evaluate the results of the optimization is to compare
simulations using the default, perturbed, and re-optimized versions of the
model.

Following the re-parameterization, we now have new values of the independent
arguments, but this is not enough to actually run the new version of the model.
Thus, the next step is to form a new model definition by updating the values of
the default soybean model. This can be accomplished using the `update_model`
function from `BioCroValidation`:

```{r form_new_models}
# Get model definition lists for the perturbed and re-parameterized versions of
# the soybean model
soybean_perturbed <- update_model(
  BioCro::soybean,
  independent_args,
  initial_guess,
  dependent_arg_function = dependent_arg_function
)

soybean_reparam <- update_model(
  BioCro::soybean,
  independent_args,
  optim_res[['par']],
  dependent_arg_function = dependent_arg_function
)
```

We can check that the three models have different values of key parameters, such
as the "dependent" argument `mrc_stem`:

```{r}
print(BioCro::soybean$parameters$mrc_stem)

print(soybean_perturbed$parameters$mrc_stem)

print(soybean_reparam$parameters$mrc_stem)
```

Now we can run each version of the model for a single year and visually compare
their outputs:

```{r comparison_plots}
# Define a helper function that runs a single model for the year 2005
run_2005 <- function(model_definition) {
  with(model_definition, {run_biocro(
    initial_values,
    parameters,
    soybean_weather[['2005']],
    direct_modules,
    differential_modules,
    ode_solver
  )})
}

# Run each model and combine the results
full_res <- rbind(
  within(run_2005(BioCro::soybean),   {model = 'Default Soybean-BioCro'}),
  within(run_2005(soybean_perturbed), {model = 'Perturbed Soybean-BioCro'}),
  within(run_2005(soybean_reparam),   {model = 'Re-parameterized Soybean-BioCro'})
)

# Plot the results
xyplot(
  Leaf + Stem + Root + Grain ~ fractional_doy,
  group = model,
  data = full_res,
  type = 'l',
  auto.key = list(space = 'top'),
  xlab = 'Day of year (2005)',
  ylab = 'Biomass (Mg / ha)'
)
```

Here we can see that while the simulated values for some tissues do not differ
much between the models, there are large differences in other tissues; for these
cases, the default and re-optimized versions are similar and the perturbed
version is much different.

## Saving the New Model Definition

A realistic parameterization takes a long time to complete, so it is important
to save the results for later use. One approach is to save the model definition
list using the `save` or `saveRDS` functions from base R. However, these options
create binary files that are not human-readable, and they cannot be easily
tracked using `git`. As an alternative, the `BioCroValidation` includes a
function called `write_model` that forms a string representing an R command that
can be called to re-create a model definition. This command string can be
written to a text file, making it easy to read and to track with `git`.

Here we apply `write_model` to the re-optimized soybean model:

```{r write_model_command}
# Convert the re-parameterized soybean model to an R command string
r_cmd_string <- with(soybean_reparam, write_model(
  'soybean_reparam',
  direct_modules,
  differential_modules,
  initial_values,
  parameters,
  ode_solver
))
```

We can view the resulting R command string:

```{r}
writeLines(r_cmd_string)
```

It can also be written to a text file:

```{r write_model_to_file, eval = FALSE}
# Save the model definition as an R file in the current working directory
writeLines(r_cmd_string, './soybean_reparam.R')
```

# Commands From This Document

```{r, eval = FALSE}
###
### Preliminaries
###

<<libraries>>

###
### Prepare inputs for `objective_function`
###

<<base_model_definition>>

<<process_tables>>

<<data_driver_pairs>>

<<post_process_function>>

<<data_definitions>>

<<independent_args>>

<<dependent_arg_function>>

<<quantity_weights>>

<<extra_penalty_function>>

###
### Create the objective function
###

<<objective_function>>

###
### Use an optimizer to choose parameter values
###

<<initial_guess>>

<<setting_bounds>>

<<run_optimizer>>

###
### Check and record the new values
###

<<compare_param>>

<<form_new_models>>

<<comparison_plots>>

<<write_model_command>>

<<write_model_to_file>>

```

# References
